Tuning for Software Analytics: is it Really Necessary?

### 2016-01-18 tuningpredictor.tex
Updates from ShareLaTeX

\section{Preliminaries}
\subsection{Issues of Tuning: Important and Ignored?}
In  other fields, the impact of tuning is well understood~\cite{Bergstra2012}. 
Yet, as argued in this section, issues of tuning  are rarely or poorly addressed
in the defect prediction literature.

The formal definition of data mining stresses that these learners are heuristic explorers
of a truly   vast space of the possible models within a data set~\cite{mitchell1982generalization}. For example, given 20 columns of boolean variables,
there are $2^{20}$ possible models. Data mining is practical since various heuristics
allow automatic algorithms to ignore most of those possibilities. While heuristic search makes data mining possible, it also means that tunings
can significantly affect what comes out of a data miner.
When we tune a data miner, what we are really doing is changing how a learner applies
its heuristics. This means tuned data miners use different heuristics, which means they ignore different possible models, which means they return different models; i.e.  {\em how} we learn changes {\em what} we learn.

@@

\subsection{An Aside}

One comment before presenting the results. The following text does not
show results for tuning on recall
or false alarms. Those goals focus on {\em only}
the  defective or non-defective modules (respectively). Hence,
when DE tunes for recall, we can achieve near
100\% recall-- but the cost of a near 100\% false alarms.
Similarly,  tuning
can achieve near zero false alarm rates by effectively turning off
the detector (when recall is zero).
Accordingly,  this paper  explores performance measures that comment on all 
target classes (i.e. precision and ``F'').

@@

That said, our tuning results show that it is time to revise
the recommendations of those papers. 
  \fig{lr} comments on the advice from Hall et al. (that LR is better than Random Forest).
 In a result that might have been predicted by Hall et al., Logistic Regression does perform better than untuned Random
Forests over 13 out of 17 data sets. 
However, it turns out that advice is sensitive to the tunings
used with Random Forest. After tuning, we find that Random Forest
is often competitive, and sometimes even better, than Logistic Regression.

@@

% list some features
\begin{table}[!b]

>>>>

\section{Digression}

Before starting, we offer the following aside.
An important principle in tuning is that
{\em you can't always get \underline{all} you want}.
In the following, we present tuning as a multi-objective optimization problem
and, with some problems, it is not always possible to optimize for every goals.
For example, the following text does not
show results for tuning on recall
or false alarms since otpimizing {\em only} for those goals can lead
to some undesirable side effects. For example: 
\bi
\item
{\em Recall} reports the percentage of  predictions that are actual examples of  what we are looking for.
When we tune for {\em recall}, we can achieve near
100\% recall-- but the cost of a near 100\% false alarms.
\item
{\em False alarms} is the percentage of other examples that are reported  (by the learner)
to be part of the targeted examples.
When we tune for {\em false alarms}, we 
can achieve near zero percent false alarm rates by effectively turning off
the detector (so the  recall falls to nearly zero).
\ei
Accordingly,  this paper  explores performance measures that comment on all 
target classes (see the  precision and ``F'' measures discussed in \fig{xxx}).

\section{Preliminaries}

\subsection{Issues of Tuning: Important and Ignored?}
In  other fields, the impact of tuning is well understood~\cite{Bergstra2012}. 
Yet, as argued in this section, issues of tuning  are rarely or poorly addressed
in the defect prediction literature.

When we tune a data miner, what we are really doing is changing how a learner applies
its heuristics. This means tuned data miners use different heuristics, which means they ignore different possible models, which means they return different models; i.e.  {\em how} we learn changes {\em what} we learn.

@@

@@

That said, our tuning results show that it is time to revise
the recommendations of those papers. 
  \fig{lr} comments on the advice from Hall et al. (that LR is better than Random Forest)L
  \bi
  \item
 In a result that might have been predicted by Hall et al.,  
 untuned Random
Forests performs comparatively worse than
 Logistic Regression. Specifically, untuned
 Random Forest performs worse than Linear regression in in 13 out of   17 data sets. 
\item
However, it turns out that advice is sensitive to the tunings
used with Random Forest. After tuning, we find that tuned Random Forest
loses to Logistic Regression in only 6 out of 17 data sets. 
\ei

@@

% list some features
\begin{table}[!t]
